Shiny Walkthrough

### 2020-06-25 analysis/shiny_walkthrough.Rmd
@marcdotson @evanwride I added in some things from my notes from the R user group/other research and added a little more code to show the basic example of a shiny app at the beginning to see the flow of how it works and looks before going into more depth on each component

@@

@@

### Row layout
```{r}
body <- dashboardBody(
  fluidRow(
# Row 1
  box(
  width = 12, # 12 width spans the entire width of the screen
  title = "Regular Box, Row 1",
  "Text inside of box"
  )),
  fluidRow(
# Row 2
  box(
  width = 12,
  title = "Regular Box, Row 2",
  "Text inside of box 2"
  )
)
)
ui <- dashboardPage(header = dashboardHeader(),
                    sidebar = dashboardSidebar(),
                    body = body
                    )

>>>>

## Shiny Outline

If you were to open a Shiny app while creating a new file in R, an outline of the an app will be shown using the Old Faithful Geyser Data. This example app shows eruption wait times in a histogram with a side panel to change the number of bins in the histogram. A simple example of what these apps are intended for, user interaction.

```{r}
## Old Faithful Geyser Example

library(shiny)

# Define UI for application that draws a histogram
ui <- fluidPage(

    # Application title
    titlePanel("Old Faithful Geyser Data"),

    # Sidebar with a slider input for number of bins 
    sidebarLayout(
        sidebarPanel(
            sliderInput("bins",
                        "Number of bins:",
                        min = 1,
                        max = 50,
                        value = 30)
        ),

        # Show a plot of the generated distribution
        mainPanel(
           plotOutput("distPlot")
        )
    )
)

# Define server logic required to draw a histogram
server <- function(input, output) {

    output$distPlot <- renderPlot({
        # generate bins based on input$bins from ui.R
        x    <- faithful[, 2]
        bins <- seq(min(x), max(x), length.out = input$bins + 1)

        # draw the histogram with the specified number of bins
        hist(x, breaks = bins, col = 'darkgray', border = 'white')
    })
}

# Run the application 
shinyApp(ui = ui, server = server)

Viewing this example can be useful to see the flow of the user interface and processes. So let's go through what those terms mean. There are essentially three steps to any Shiny App:

1. Create the User interface -- __ui__
2. Create the processes -- __server__
3. Run the app -- __shinyApp__

The two main parts of the Shiny app are the __ui__ and the __server__. These objects are the arguments used in the function to run the app, __shinyApp(ui, server)__. We will create an ui and server object for these arguments and name them what they are, _ui_ and _server_. This will help us from mixing up them up and make our lives easier.

## Shiny and Shinydashboard

We will mostly be talking about shinydashboard in this walkthrough. There is no reason to worry as the two packages are essentially the same, but shinydashboard puts your code into an already styled theme in the ui without having to write the code yourself.

@@

The __ui__ object controls the layout and appearance of the app. This includes formatting, color, text, input panels, main panels, etc. (maybe go into detail here). ui writes your code into html for you. Alternatively, you could use the html functions as well.

For shinydashboard we design parts of the ui and then combine it together in a function called dashboardPage(). To keep things simple, we will go through each of the main parts individually. Then show how they can be combined in this dashboardPage() to make the comeplete user interface.

@@

### Row layout
```{r}
body <- dashboardBody(
  fluidRow(
# Row 1
  box(
  width = 12, # 12 width spans the entire width of the screen
  title = "Regular Box, Row 1",
  "Text inside of box"
  )),
  fluidRow(
# Row 2
  box(
  width = 12,
  title = "Regular Box, Row 2",
  "Text inside of box 2"
  )
)
)
